---
title: "Installing Bioconductor"
author: "Kasper D. Hansen"
---

```{r front, child="front.Rmd", echo=FALSE}
```

## Installing Bioconductor

The one true way to install Bioconductor is by using the `BiocManager` CRAN package, which can be installed using the typical R install.packages() method. Bioconductor used to be installed using biocLite, but since version 3.8 (for R 3.5.0) that is deprecated.

```{r BiocManager, eval=FALSE}
install.packages("BiocManager")
```

The first time you run the script without arguments, it will install a core set of Bioconductor packages.

```{r BiocManager1, eval=FALSE}
BiocManager::install()
```

When you run this script, it will autodetect if any of your installed packages are out of date; it will aggressively ask you to update your packages.

Because of this, the way you update a Bioconductor installation, is just by running `biocLite()` without any argument.

You can check if your installation is fully up-to-date, by running `biocValid()`; it will return `TRUE` if everything is current.

You install a new package by using `biocLite` with the package name, for example
```{r BiocManager2, eval=FALSE}
BiocManager::install("limma")
```

The reason why you want to use `BiocManager::install` - and only this function - to install and update Bioconductor, is because one of the top problems users have is when they mix and match Bioconductor packages from different releases.  Using `BiocManager` ensures that everything is synchronized.

The way you update Bioconductor itself when a new release comes out, is by updating R itself and then run `BiocManager::install()`.

There are more comprehensive installation instructions on the [Bioconductor site](http://bioconductor.org/install).

```{r back, child="back.Rmd", echo=FALSE}
```
